### 2024-04-15 docs/projects/datavis/ggplot/study_session_20240225.qmd
ggplot - rerendered

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM x06c5570df1b44c78]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

@@

<image id="image487" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>

@@

  <use xlink:href="#image487"/>

@@

<g id="surface483">

>>>>

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [[$ .MEM x04d1ec48fa8b4a52]],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ year]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["year"]}}

@@

<image id="image486" width="1" height="300" xlink:href="data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAAAEAAAEsCAIAAACNMk6CAAAABmJLR0QA/wD/AP+gvaeTAAAAjklEQVQ4jaWTQRKAMAgDd3ik//R1HuOlji3SjNYjhZAEKNt+BCgQIRRIAQRSi2l5hdr79/q1fqBQVw+ErvyipqGH5eh7fNFJi1M+9bC8OT/lrTD9fNYwT/0FpvQzwVju0eObndsd/uUa7qX2NffqNE5w7j7dbCudpXbj2ehX0n3f0ot5pX9/1xkPj79W8p41NH/nSHk1sQAAAABJRU5ErkJggg=="/>

@@

  <use xlink:href="#image486"/>

@@

<g id="surface482">
